Comparing Early Evolution of Flames in X-ray Bursts in Two and Three Dimensions

### 2023-03-26 xrb3/paper.tex
manually make the figure captions bigger

\begin{figure}[t]
\centering
%\epsscale{0.75}
\plotone{abar_top_stack}
%\epsscale{1.0}
\caption{\label{fig:vr_abar} Volume rendering of the three-dimensional XRB
simulation showing the mean molecular weight, $\bar{A}$.  The flame is viewed
from above. The panels show the state at 10 ms, 20 ms, and 40 ms (from top to bottom).}
\end{figure}

>>>>

\begin{figure}[t]
\centering
%\epsscale{0.75}
\plotone{abar_top_stack}
%\epsscale{1.0}
\caption{\label{fig:vr_abar} Volume rendering of the three-dimensional XRB
simulation showing the mean molecular weight, $\bar{A}$.  The flame is viewed
from above. The panels show the state at 10 ms, 20 ms, and 40 ms (from top to bottom).
The colorbar shows the value of $\bar{A}$ together with the opacity assigned for
that value---this allows us to bring out some structure in the rendering.}
\end{figure}
